### 2020-10-09 Analysis/Code/Paper.Rmd
Draft 1.0

# Literature Review

This paper contributes to several closely related literatures in economics and marketing. The oldest of these is the literature investigating the impact of online consumer reviews on sales. An extensive review of the studies focusing on this topic and their meta-analysis is provided, for example, by @Floyd14. 
<!-- Researchers have analyzed multiple online platforms, selling different products and employing different review systems, and produced, overall, conflicting evidence on whether reviews improve sales, and if so, through which channels. The major identification challenge stems from the fact that better reviews might simply be manifestations of consumer preferences for certain products, or reflect higher quality of the underlying products. As preferences and quality are unobserved and, in general, fluid, researchers have struggled to come up with convincing identification strategies. -->
In a seminal contribution in this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales. A similar approach applied to the same market was recently used by @ReimersWaldfogel20, who reaffirm the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews. @ZhuZhang10 exploit differences between two different video games consoles rather than websites, and find that review ratings matter only for less popular games.

For identification, the difference-in-differences approach relies on the existence of several comparable platforms, and assumes that the unobserved platform-specific tastes
for those platforms are fixed. Another approach to identification exploits the rounding of the review data that platforms use to produce simple visual review labels. For example, Yelp.com, a popular restaurant comparison service, assigns 4 stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but 4.5 stars to restaurants with an average score between 4.25 and 4.74.  @AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue. @SorokinStevens20 applies a similar approach to the video games market and also finds that better review labels increase sales, albeit raising some concerns about the validity of the approach. In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from the video games' usage data. The present paper supplements the panel methods in @SorokinStevens20 by offering a structural way to estimate the effect of reviews on sales in the absence of direct sales data.

With benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits. There are several ways firms can affect their online reviews. One is review fraud. @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves. @LucaZervas16 provide similar evidence for restaurants on Yelp. A more honest way for a firm to influence reviews is by assuming an active approach to review management, and to publicly respond to reviews published online. @GuYe14 provide evidence that consumers who had left a negative review about their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management. @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future. This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes. @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to. In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity. The idea is that consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.

Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews. Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle. Another strand of literature is studying whether different kinds of promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a Groupon price promotion. They present evidence that customers attracted by the promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher, which can explain the reasons behind their dissatisfaction. Thus, the paper cautions against running price promotions in an attempt to poach new customers and improve the online reputation. @Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews. In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and they provide evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it.

My paper contributes to this literature in several ways. First, I present evidence from a market that was not previously studied in the literature, and confirm that reviews left on a price promotion are not favorable to businesses. Second, I show that, nevertheless, firms can successfully manage their online reputation through pricing, by going on a discount when they are close to upgrading their review tier. A study similar in spirit to mine is that of @Zegners17, who argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap". However, this study also finds that books are more likely to solicit negative feedback when sold for free, which somewhat undermines the strategy. Similar to @ByersEtAl12, @Zegners17 argues that purchasers of free books differ from the purchasers of regular books in their observable characteristics, and explains the negativity of the reviews by the selection effect.

# Institutional Setting and Data

@@

# Empirical Model of Demand
\label{demandSection}
\textcolor{red}{Write a small introduction here.}

@@

\textcolor{red}{Add an introduction}

@@

# Selection and Variance Effects

@@

I start off by estimating the average probabilities of leaving a good and a bad review in the population, and by using the estimates to test hypotheses formulated in (\ref{hyp1}) and (\ref{hyp2}). I use two sets of covariates to explain these probabilites. The baseline set of covariates, $w_{it} = [1, disc_{it-k}]'$, only allows the probability of a like or a dislike to change if a discount is in place. The theory behind this choice is that reviews reflect the average perception of quality by the consumers. As my sample was selected to only include products with constant quality, this perception should only change if different types of consumers are buying the product. Consumers buying on a discount are paying a lower price, and thus could be different from consumers paying the whole price. This is the selection effect of discounts on reviews. I also acknowledge the possibility that there could be a selection over time, when early buyers are very different from late buyers. Similarly, the perception of quality might be deteriorating over time as new games, with potentially better characteristics, are coming out. For this reason, the second set of covariates also adds two variables measuring age: $w_{it} = [1, disc_{it-k}, young_{it}, old_{it}]'$, where $young_{it}$ is a dummy indicating that the game is less than 2 weeks old, and $old_{it}$ is a dummy indicating that the game is more than a year old. The estimates are presented in Table \ref{reviewEstimates}.

@@

To strengthen this point, I use the difference in the valence of reviews on and off a discount to measure the selection effect at the game level. With such estimates at hand, I can revisit my regression of discounts on proximities to transitions (\ref{potTransitionsReg}) controlling for the selection effect. In the identification section I showed how one can estimate the like and dislike rates on the product level. Using these estimates, the selection effect can be measures as the difference between the expected review scores on and off a discount:

@@

Figure \ref{scoreDifPlot} depicts the distribution of $\widehat{\Delta score_{i}}$, the sample counterpart of this measure. In line with the hypothesis test of the sign of the selection effect in the sample, the histogram is centered around zero. Estimates of $\Delta score_{i}$ vary in their precision from game to game, as games that spent less little time in the sample and/or on discounts would naturally have noisier estimates. However, the distribution appears to be well-behaved.

@@

I estimate (\ref{potTransitionsHeteroReg}) by OLS (without the fixed effect term $f_i$) and by the within-estimator. The results are presented in Table \ref{scoreDifTransDiscReg} (the controls are omitted for brevity). The least squares estimates in column (OLS) are mainly presented to check the correlations in the data. Games that tend to receive better reviews on discounts discount more. However, the selection effect is not significant in both specifications. Crucially, in the preferred specification (FE) I find that $\beta^-_0 < 0$, and $\beta^+_0 > 0$. Once the variation in the selection effect is controlled for, I obtain the coefficients measuring the impact of the variance effect on discounting decisions, and the signs align with the theory. Their sizes are also quite economically meaningful, suggesting that, in the absence of the selection effect, games close to a positive transition are \textcolor{red}{number}% more likely to go on a discount, and games close to a negative transition are \textcolor{red}{number}% less likely to go on a discount.

>>>>

In his book “Economics for the Common Good” Jean Tirole proclaims the economy we live in to be governed by “Economics of Attention” [-@Tirole17]. A simple search for wine glasses on Amazon.com results in more than 5,000 options, leading to a choice problem that is virtually impossible to solve satisfactory without guidance. Such guidance is provided by different types of recommendation systems. Many marketplaces or third party websites allow consumers to review products and services that they purchased, and aggregate these reviews into a rating, greatly facilitating the comparison between the alternatives. These ratings are often given a simple graphical representation; for example, a number of stars between 0 and 5 is a common way to split the alternatives into *review tiers*. Such review tiers are used to review household items (Amazon), movies (IMDb), restaurants (Yelp), doctors (RateMDs), and many other products and services. Both an extensive literature in marketing, and anecdotal evidence from these markets, suggest that good reviews are at the very least important for the success of the business. Not surprisingly, firms assume an active approach to managing their reviews. Firms solicit reviews from their clients, publicly respond to reviews, and even leave fake reviews for themselves or their competitors.

In this paper I study a novel form of review management. I show that firms can use discounting in order to facilitate *transitions* between review tiers. Imagine a product that is several good reviews short of obtaining an additional star. I ask: would it be profitable for such a product to run a price promotion?  With a help of a stylized model, I identify two effects that influence this decision: the *selection* effect and the *variance* effect. Customers who purchase the good on a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews. If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount. Whether the selection effect is positive or negative is an empirical question, and I answer this question with my data. The variance effect reflects the idea that a product that is close to a transition is willing to gamble on upgrading its review tier. Extra positive reviews catapult it to the next review bin, which promises higher sales, while a few negative reviews would not affect its review status and sales much. While extra variance is good for products that are on the verge of a tier upgrade, it could be harmful for products that are close to sliding one review tier down. Fearing to lose that precious star, such products would prefer to delay running a price promotion, unless the selection effect is positive and strong.

To quantify all these effects, I analyze data from Steam, a major marketplace for computer video games. I build and estimate a simple structural model of demand and reviewing behavior on Steam. The demand part of the model lays the groundwork for my analysis. I confirm the importance of better review tiers for sales on Steam, finding a premium of as high as 10% of being in the best bin, and a penalty of up to 13% for not having reviews, compared to a mediocre review tier. My estimates also highlight how impactful discounts are in this market, with an average discount being accompanied by a 25% spike in sales. Thus, firms on Steam have both the ability to use discounts to attract new users, and the incentives to upgrade their review tiers, given the differential contribution of various tiers on sales. I further document that these incentives translate into action. I find that products that are close to upgrading their review tier are 4-9% more likely to be on a discount, and I find some evidence that proximity to a downward transition decreases the probability to be on a discount by up to 4%.

To learn more about the relative contributions of the variance and the selection effects to the observed behavior, I estimate the review part of my structural model. I estimate the effect of discounts on the probabilities to leave positive and negative reviews. I find no evidence that the selection effect is positive on Steam, meaning that, on average, reviews left during a price promotion are not more favorable than the ones left outside of a price promotion. Thus, I attribute firms' behavior to the variance effect. While this effect is hard to test directly, I provide some further indirect tests of its impact on the discounting behavior around review tier transitions. I estimate the size of the selection effect at the product level, and “control” for it in my regressions of discounts on proximities to transition. I find that, in the absence of the selection effect, products that are close to a review downgrade are significantly less likely to discount, which is consistent with the idea that the variance effect is negative for such products. I also provide novel evidence that consumers who buy the product during a price promotion are more likely to leave a review, which speaks to the mechanism through which “variance” is created by a discount.

## Literature Review

While some of my findings are new and interesting on their own, others are best measured against the literatures in economics and marketing that I contribute to. The oldest of these is the literature investigating the impact of online consumer reviews on sales. An extensive review of the studies focusing on this topic and their meta-analysis is provided, for example, by @Floyd14. 
<!-- Researchers have analyzed multiple online platforms, selling different products and employing different review systems, and produced, overall, conflicting evidence on whether reviews improve sales, and if so, through which channels. The major identification challenge stems from the fact that better reviews might simply be manifestations of consumer preferences for certain products, or reflect higher quality of the underlying products. As preferences and quality are unobserved and, in general, fluid, researchers have struggled to come up with convincing identification strategies. -->
In a seminal contribution in this literature, @ChevalierMayzlin06 uses a difference-in-differences approach, exploiting the differences in reviews for the same books across Amazon.com and Barnesandnoble.com, to argue that better reviews causally improve sales. A similar approach applied to the same market was recently used by @ReimersWaldfogel20, who reaffirm the importance of reviews for sales of books and quantify the welfare implications of the informational content of consumer reviews. @ZhuZhang10 exploit differences between two different video games consoles rather than websites, and find that review ratings matter only for less popular games.

For identification, the difference-in-differences approach relies on the existence of several comparable platforms, and assumes that the unobserved platform-specific tastes
for those platforms are fixed. Another approach to identification exploits the rounding of the review data that platforms use to produce simple visual review labels. For example, Yelp.com, a popular restaurant comparison service, assigns 4 stars to restaurants that have an average review score between 4 and 4.24 (out of 5), but 4.5 stars to restaurants with an average score between 4.25 and 4.74.  @AndersonMagruder12 and @Luca16 develop a regression discontinuity approach exploiting this rounding to show that an additional half-star on Yelp.com increases restaurants' traffic and revenue. In studies relying on a discontinuity for identification, it is crucial that assignment around thresholds is as good as random. Unlike the settings in which the variable that is measured against the cutoff is realized once (a student takes the test once, and either earns an “A” or a “B”), products carry their review scores from day to day. If one product is slightly below the cutoff and has 4 stars, and another product is slightly above the cutoff, why would the former not try to do something to cross the cutoff, especially if better review bins are more lucrative? My paper asks precisely that question, and shows that such concerns are well-founded. However, I do not study the implications of such behavior for a regression discontinuity approach used in the aforementioned papers.

@SorokinStevens20 raises other concerns about the validity of the regression discontinuity approach in studying the causal effect of reviews on outcomes. To my knowledge, it was the first paper to use Steam as the object of its analysis. In the absence of direct sales data, @SorokinStevens20 uses a particular regression specification that extracts the information on sales from the video games' usage data. I inherit the data from that paper, but confront the absence of sales data in a more hands-on way. I make assumptions about the gaming patterns of the users of the games in my sample, and formulate a structural model of the data generating process. With the help of that model, I manage to extract information on product sales from usage data only. I also compare the estimates of the structural model with the ones obtained by its simpler regression analog, which happen to be quite similar. The last improvement of the present study over @SorokinStevens20 is that I employ all the relevant review tiers present on Steam, while in earlier work the regression discontinuity approach dictated the focus on a certain subset of review labels.

With benefits of having good reviews come the incentives to influence the reviews in order to reap those benefits. There are several ways firms can affect their online reviews. One is review fraud. @Mayzlin14 provides evidence that small hotel owners leave negative reviews for their competitors, and good reviews for themselves. @LucaZervas16 provide similar evidence for restaurants on Yelp. A more scrupulous way for a firm to influence reviews is by assuming an active approach to review management---for instance, by publicly responding to the reviews it receives. @GuYe14 provide evidence that consumers who had left a negative review about their hotel experience in the past were more likely to leave a positive review of the same hotel after a future stay if their previous review was responded to by the management. @XieEtAl17 shows that lengthy in-depth managerial responses to negative reviews are associated with better financial performance in the future. This literature has also been concerned with how consumers change their reviewing behavior when managers start responding to reviews, essentially moving from studying individual responses to describing equilibrium outcomes. @ProserpioZervas17 argues that hotels responding to bad reviews experience an increase in both the valence and the volume of their reviews, attributing it to consumers' reluctance to leave short indefensible reviews in a situation when they can be responded to. In somewhat contradictory findings,  @ChevalierEtAl18 finds the opposite effect in the same market, arguing that managerial responses encourage negative review activity. The idea is that consumers get a signal that the firm is “listening” to them, and are then stimulated to leave negative reviews that they deem more influential.

Direct ways of managing online reputation discussed above, however, are not the only avenues through which businesses can affect their reviews. Reviews are left by customers, and the happier they are, the better reviews they should leave, at least in principle. Another strand of literature is studying whether price promotions have an effect on firms' online reputation. In a seminal study, @ByersEtAl12 documents that restaurants receive substantially worse reviews after running a price promotion through Groupon, a promotion service. In other words, @ByersEtAl12 documents a negative selection effect on Yelp. It presents evidence that customers attracted by a promotion are different from regular customers, and that they are more likely to be trying out a new restaurant or cuisine while using the Groupon voucher. This difference can explain the reasons behind the dissatisfaction of the Groupon customers. @Li16 confirms the finding in the same setting, but finds that restaurants with fewer and worse reviews can actually benefit from participating in a Groupon promotion. There are a couple of other studies that dispute the negativity of the selection effect. @ZhuEtAl19 shows that customers who received a discount leave more positive, albeit less informative, reviews. In an experimental study on Ebay, @CabralLi15 also finds that offering a rebate for leaving (any) review significantly decreased the likelihood of negative feedback, and it provides evidence that this is due to reciprocity on the side of the clients, rather than the differences between customers buying with a rebate and without it. My study contributes to this debate by documenting the absence of a positive selection effect in a new market. Additionally, my paper is the first to focus on discrete changes in review tiers that follow the discounts, instead of studying the continuous effect of a discount on the review score.

Based on its findings, @ByersEtAl12 cautions businesses against running price promotions in an attempt to poach new customers and improve their online reputation. To the extent that managers and scholars perceive promotions to be an effective way of managing reputation, this finding presents a puzzle. A similar puzzle is encountered by @Zegners17, which argues that less-known authors of eBooks on a crowded online marketplace are more likely to give their books out for free in order to build reputation and escape the "zero reviews trap". While the idea is intuitive, the findings are that products employing free pricing are more likely to solicit *negative* feedback when sold for free, which somewhat undermines the strategy. I provide a novel mechanism--- the variance effect---that could explain the prevalence of price promotions when the selection effect of reviews is negative. The variance effect would explain the behavior observed in @Zegners17 as follows: if a  product with no reviews is already doomed, it would find it profitable to sell for free even if the probability to solicit favorable reviews is small. After all, sales can not fall below zero, but the upside of accumulating some positive reviews and escaping the trap is substantial.

The rest of this paper is organized as follows. Section \ref{dataSection} describes the institutional setting and the data I use. Section \ref{demandSection} develops and estimates the structural model of demand and gaming activity on Steam. The technical nature of the material in this section contributes greatly to its size, but goal of this section is simply to quantify the importance of different review tiers on sales, and to show that discounts are effective in attracting new customers. The main findings are described in  Section \ref{descriptiveEvidence}. It opens with a stylized model of discounting for a product close to a review tier transition, and introduces the selection and the variance effects. The section proceeds by establishing that such discounting behavior takes place in the data. Section \ref{selectionEffect} supplements the demand model from Section \ref{demandSection} by a model of reviewing activity, and estimates its parameters in order to quantify the relative contributions of the selection and the variance effect to the observed patterns of discounting around review transitions. Section \ref{conclusion} concludes.

# Institutional Setting and Data 
\label{dataSection}

@@

# Empirical Model of Demand
\label{demandSection}

In this section I develop and estimate a simple structural model of demand an gaming activity on Steam. I discuss at length the assumptions and the interpretation of the parameter estimates. However, the main takeaway from this section is simple: better review labels improve sales, and discounts are important drivers of sales on Steam. These two facts form the foundation of my main analysis that will be carried out in Section \ref{descriptiveEvidence}, where I will show that firms use discounts to attract new reviews and to transition to more lucrative review tiers. I will further extend the model from this section in Section \ref{selectionEffect}.

@@

@@

# Selection and Variance Effects
\label{selectionEffect}

@@

I start off by estimating the average probabilities of leaving a good and a bad review in the population, and by using the estimates to test hypotheses formulated in (\ref{hyp1}) and (\ref{hyp2}). I use two sets of covariates to explain these probabilities. The baseline set of covariates, $w_{it} = [1, disc_{it-k}]'$, only allows the probability of a like or a dislike to change if a discount is in place. The theory behind this choice is that reviews reflect the average perception of quality by the consumers. As my sample was selected to only include products with constant quality, this perception should only change if different types of consumers are buying the product. Consumers buying on a discount are paying a lower price, and thus could be different from consumers paying the whole price. This is the selection effect of discounts on reviews. I also acknowledge the possibility that there could be a selection over time, when early buyers are very different from late buyers. Similarly, the perception of quality might be deteriorating over time as new games, with potentially better characteristics, are coming out. For this reason, the second set of covariates also adds two variables measuring age: $w_{it} = [1, disc_{it-k}, young_{it}, old_{it}]'$, where $young_{it}$ is a dummy indicating that the game is less than 2 weeks old, and $old_{it}$ is a dummy indicating that the game is more than a year old. The estimates are presented in Table \ref{reviewEstimates}.

@@

To strengthen this point, I use the difference in the valence of reviews on and off a discount to measure the selection effect at the game level. With such estimates at hand, I can revisit my regression of discounts on proximities to transitions (\ref{potTransitionsReg}) controlling for the selection effect. In the identification section I showed how one can estimate the like and dislike rates on the product level. Using these estimates, the selection effect can be measured as the difference between the expected review scores on and off a discount:

@@

Figure \ref{scoreDifPlot} depicts the distribution of $\widehat{\Delta score_{i}}$, the sample counterpart of this measure. In line with the hypothesis test of the sign of the selection effect in the sample, the histogram is centered around zero. Estimates of $\Delta score_{i}$ vary in their precision from game to game, as games that spent less time in the sample and/or on discounts would naturally have noisier estimates. However, the distribution appears to be well-behaved.

@@

I estimate (\ref{potTransitionsHeteroReg}) by OLS (without the fixed effect term $f_i$) and by the within-estimator. The results are presented in Table \ref{scoreDifTransDiscReg} (the controls are omitted for brevity). The least squares estimates in column (OLS) are mainly presented to check the correlations in the data. Games that tend to receive better reviews on discounts discount more. However, the selection effect is not significant in both specifications. Crucially, in the preferred specification (FE) I find that $\beta^-_0 < 0$, and $\beta^+_0 > 0$. Once the variation in the selection effect is controlled for, I obtain the coefficients measuring the impact of the variance effect on discounting decisions, and the signs align with the theory. Their sizes are also quite economically meaningful, suggesting that, in the absence of the selection effect, games close to a positive transition are \textcolor{red}{number} `r round(100*reg3$coefficients["pos.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% more likely to go on a discount, and games close to a negative transition are \textcolor{red}{number}  `r -round(100*reg3$coefficients["neg.treatmentTRUE"]/panel[, mean((discount > 0), na.rm=T)])`% less likely to go on a discount.

# Conclusion
\label{conclusion}

In this paper I document a novel mechanism through which firms use pricing to manage their online reviews. Using data from Steam, a major digital marketplace for computer video games, I show that firms discount their products in order to facilitate transitions between review tiers. Products that are close to upgrading their review tier are 4-9% more likely to be on a discount, while products close to deteriorating their review tier are up to 4% less likely to discount, albeit this effect is less significant.

I identify two channels that can make such behavior profitable: the *selection* effect and the *variance* effect. Customers who purchase the good on a discount are likely to be different from the ones who pay the full price, and could potentially leave different reviews. If such reviews tend to be more favorable, then the induced positive selection effect creates incentives for the product to go on discount, regardless of whether the product is about to upgrade or downgrade its review tier. There is some disagreement in the literature about the sign of the selection effect. I contribute by showing that on Steam the effect is not positive.

The variance effect reflects the asymmetry between the successful and the unsuccessful discounting campaign, as measured by the valence of the new reviews. A product close to moving one review tier up benefits greatly from a good realization, while a bad one does not change its review tier much. On the other hand, a product that is close to sliding into a worse tier, if averse to a bad outcome, and would benefit less in absolute value from a good outcome. While I manage to test the selection effect directly, I have to test the variance effect by trying to falsify the predictions that follow from it. My strongest test is given by the prediction that, in the absence of a positive selection effect, the variance effect has to make a product on the verge of deteriorating its reviews less likely to discount. When I control for the size of the selection effect, I find that the aforementioned decline in probability of discounting goes from being 4% and weakly significant to 6% and highly significant. I also leverage my unique data and  structural model to document that consumers are more likely to leave reviews when they buy on a discount, which indirectly supports the importance of the variance effect.

I develop a structural model of demand and product usage, that allows me to make statements about sales using data on usage. This model extends the approach of @SorokinStevens20. Using this model, I provide new estimates of the causal effect of reviews on sales on Steam. Being in the best review bin carries a premium of up to 10% compared to a mediocre review tier; having no reviews has a negative effect of up to 13%. In a methodological contribution, I compare the performance of my structural model with its simpler cousin from @SorokinStevens20. While there are some important differences between the two sets of estimates, I find the part concerning the effect of review bins on sales to be fairly similar.
